Certified Symbolic Transducer with the Application of String Solver

### 2025-01-21 Paper/main.tex
add Automata

@@

Figure \ref{fig-def-product-correct} shows the correctness of the product operation and Figure \ref{fig-def-output} contains the definitions of \texttt{outputE} and \texttt{outputL} that are used in Lemma \texttt{productT\_correct}.
The two assumptions define the constraints of the function \texttt{F}.

>>>>

We highlight our formulization with the following points.
(1) Efficiency, the algebraic representation
support compressed storage of transition labels and efficiency checking
of membership.
(2) Extensible, the refinement based formulization allows the extension
of the SNFA to support different theories of transition labels.

@@

Figure \ref{fig-def-product-correct} shows the correctness of the product operation and Figure \ref{fig-def-output} contains the definitions of \texttt{outputE} and \texttt{outputL} that are used in Lemma \texttt{productT\_correct}.
The two assumptions define the constraints of the function \texttt{F}.
The conclusion in \textcolor{blue}{\texttt{show}} illustrates 
that the language equivalence between the production definition and mathematical semantics.
